### 2019-11-22 3_implementation.tex
Now under the limit.

We provide two MPI~\cite{MPI} implementations, written in the style of
communicating sequential processes (CSP) and bulk synchronous
programming (BSP), respectively. An excerpt from the CSP
implementation is shown in Listing~\ref{lst:code-sample}. The BSP
implementation uses \lstinline[language=C++]{MPI_Barrier} to enforce
boundaries between phases.

@@

We performed extensive experiments to verify that no
extraneous factors interfered with our Spark measurements. We
disabled logging, ensured no RDDs are written
to disk, confirmed there is no measurable overhead due to JNI
calls from Java to C or due to the serialization of data structures, and cross-checked results with known cases
that hit optimal task throughput in Spark.

>>>>

We provide two MPI~\cite{MPI} implementations, written in the style of
communicating sequential processes (CSP) and bulk synchronous
programming (BSP). An excerpt from the CSP
implementation is shown in Listing~\ref{lst:code-sample}. The BSP
implementation uses \lstinline[language=C++]{MPI_Barrier} to enforce
boundaries between phases.

@@

We performed extensive experiments to verify that no
extraneous factors interfered with our Spark measurements. We
disabled logging, ensured no RDDs are written
to disk, confirmed there is no measurable overhead due to JNI
calls from Java to C or due to serializing data, and cross-checked results with known cases
with optimal scheduler throughput.
